Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-10-11 paper.qmd
Updated Figure 10

distance_points <- ggplot(
  distance_two_curvy_dist, 
  aes(x = as.numeric(bin),
      y = dist_highd)) +
  geom_point(alpha = 0.5) +
  #geom_jitter() +
  scale_x_continuous(breaks = sort(unique(as.numeric(distance_two_curvy_dist$bin))),
                     labels = c(
                       expression(a[1]),
                       expression(2*a[1]),
                       expression(3*a[1]),
                       expression(4*a[1]),
                       expression(5*a[1]),
                       expression(6*a[1]),
                       expression(7*a[1]),
                       expression(8*a[1])
                     )) +
  # geom_vline(xintercept = 2,
  #            linetype="solid",
  #            color = "#bdbdbd",
  #            linewidth=1) +
  # geom_vline(xintercept = 4.5,
  #            linetype="solid",
  #            color = "#bdbdbd",
  #            linewidth=1) +
  ylab(expression(d^{(7)})) +
  xlab(expression(d^{(2)})) +
  #ggtitle("(a)") +
  theme_minimal() +
  theme(aspect.ratio = 0.75,
        panel.border = element_rect(fill = 'transparent'),
        plot.title = element_text(size = 12, hjust = 0.5, vjust = -0.5),
        panel.grid.major.x = element_blank(),
        axis.ticks.x = element_line(),
        axis.ticks.y = element_line())

@@

highd_error_2d_mnist <- error_df |>
  ggplot(aes(x = tSNE1,
             y = tSNE2,
             colour = sqrt_row_wise_abs_error)) +
  geom_point(alpha=0.2) +
  scale_colour_continuous_sequential(palette = "Blues") +
  geom_rect(aes(xmin = 0.8, xmax = 0.9, ymin = 0.45, ymax = 0.6),
               fill = "transparent", color = "#000000", linewidth = 0.7) +
  geom_rect(aes(xmin = 0.75, xmax = 0.85, ymin = 0.8, ymax = 0.95),
               fill = "transparent", color = "#e41a1c", linewidth = 0.7)  +
  geom_rect(aes(xmin = 0.45, xmax = 0.55, ymin = 0.45, ymax = 0.6),
               fill = "transparent", color = "#4daf4a", linewidth = 0.7)  +
  geom_rect(aes(xmin = 0.7, xmax = 0.8, ymin = 0.25, ymax = 0.4),
               fill = "transparent", color = "#984ea3", linewidth = 0.7) 
  # scale_colour_brewer(
  #   type = "seq",
  #   palette = 1
  # ) #+ 
  # theme(
  #     legend.position = "bottom",
  #     legend.text = element_text(size = 10),          # Increase legend text size
  #     legend.key.size = unit(1, "lines")              # Increase size of legend keys
  # ) +
  # guides(
  #     color = guide_legend(
  #         override.aes = list(size = 2.5, alpha = 1)      # Increase point size and opacity in legend
  #     )
  # ) 
```

>>>>

distance_points <- ggplot(
  distance_two_curvy_dist, 
  aes(x = distance,
      y = dist_highd)) +
  geom_point(alpha = 0.5) +
  #geom_jitter() +
  # scale_x_continuous(breaks = sort(unique(as.numeric(distance_two_curvy_dist$bin))),
  #                    labels = c(
  #                      expression(a[1]),
  #                      expression(2*a[1]),
  #                      expression(3*a[1]),
  #                      expression(4*a[1]),
  #                      expression(5*a[1]),
  #                      expression(6*a[1]),
  #                      expression(7*a[1]),
  #                      expression(8*a[1])
  #                    )) +
  # geom_vline(xintercept = 2,
  #            linetype="solid",
  #            color = "#bdbdbd",
  #            linewidth=1) +
  # geom_vline(xintercept = 4.5,
  #            linetype="solid",
  #            color = "#bdbdbd",
  #            linewidth=1) +
  ylab(expression(d^{(7)})) +
  xlab(expression(d^{(2)})) +
  #ggtitle("(a)") +
  theme_minimal() +
  theme(aspect.ratio = 0.75,
        panel.border = element_rect(fill = 'transparent'),
        plot.title = element_text(size = 12, hjust = 0.5, vjust = -0.5),
        panel.grid.major.x = element_blank(),
        axis.ticks.x = element_line(),
        axis.ticks.y = element_line())

@@

highd_error_2d_mnist <- error_df |>
  ggplot(aes(x = tSNE1,
             y = tSNE2,
             colour = sqrt_row_wise_abs_error)) +
  geom_point(alpha=0.2) +
  scale_colour_continuous_sequential(palette = "YlOrRd", n_interp = 20) +
  geom_rect(aes(xmin = 0.8, xmax = 0.9, ymin = 0.45, ymax = 0.6),
               fill = "transparent", color = "#000000", linewidth = 0.7) +
  geom_rect(aes(xmin = 0.75, xmax = 0.85, ymin = 0.8, ymax = 0.95),
               fill = "transparent", color = "#e41a1c", linewidth = 0.7)  +
  geom_rect(aes(xmin = 0.45, xmax = 0.55, ymin = 0.45, ymax = 0.6),
               fill = "transparent", color = "#4daf4a", linewidth = 0.7)  +
  geom_rect(aes(xmin = 0.7, xmax = 0.8, ymin = 0.25, ymax = 0.4),
               fill = "transparent", color = "#984ea3", linewidth = 0.7) 
  # scale_colour_brewer(
  #   type = "seq",
  #   palette = 1
  # ) #+ 
  # theme(
  #     legend.position = "bottom",
  #     legend.text = element_text(size = 10),          # Increase legend text size
  #     legend.key.size = unit(1, "lines")              # Increase size of legend keys
  # ) +
  # guides(
  #     color = guide_legend(
  #         override.aes = list(size = 2.5, alpha = 1)      # Increase point size and opacity in legend
  #     )
  # ) 
```
